%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Groupon} % Organization
    {Palo Alto, United States} % Location
    {Jul. 2015 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Migrated the checkout and user auth flow out of a monolothic app to a microservice oriented architecture that runs small specialized Node.js apps}
        \item {Migrated International web platforms to US platforms}
        \item {Refactored confirmation/receipt page UX-wise - CSS and JS was remade}
        \item {Implemented Apple Pay and PayPal for checkout web client for desktop and touch}
        \item {Migrated checkout and user session web apps logging searches from splunk to ELK}
        \item {Integrated ELK searches into wavefront}
        \item {Led touch redesign project for confirmation page - frontend stack was redux and preact}
        \item {Migrated integration tests from PhantomJS to Headless Chrome on Dockerized Alpine images for Jenkins CI}
        \item {Built and led magic link Frontend implementation as an alternate authentication method}
        \item {In charge of performance reporting and improvements for login web app}
        \item {Migrated on-prem login app to AWS}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Needish} % Organization
    {Santiago, Chile} % Location
    {Mar. 2012 - Jul. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed solutions for the web platform, tech used was PHP and CakePHP.}
        \item {In charge of email deliverability with Sendgrid and ReturnPath.}
        \item {Migrated user accounts from EMEA platform to Needish platform, worked on a ETL to achive that.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Dreamside} % Organization
    {Iquique, Chile} % Location
    {Sep. 2011 - Mar. 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a service that calculates monthly revenue of the company (for "Teck" Mining Company)}
        \item {Deliver solutions such as fixes and new features to their legacy systems, written in ASP}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer - Freelancer} % Job title
    {Meaculpa's Liquor Store Chain} % Organization
    {Iquique, Chile} % Location
    {Mar. 2008 - May. 2008} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed REST synchronization API for distributed POS management.}
        \item {Developed administration web application system, written in Python using Django.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer - Intern} % Job title
    {Universidad Arturo Prat} % Organization
    {Iquique, Chile} % Location
    { Jan. 2008 - Feb. 2008} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Created a web portal for alumni, that displays their class information. Tech used: PHP and ORACLE }
      \end{cvitems}
      %\begin{cvsubentries}
      %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
      %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
      %\end{cvsubentries}
    }

%---------------------------------------------------------
\end{cventries}
